\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage{pmboxdraw}
    \usepackage[T1]{fontenc}
    \usepackage[margin=1in]{geometry}
    \usepackage{xcolor}
    \usepackage{soul}
    \usepackage{xpatch}
    \usepackage{hyperref}
    \hypersetup{
        colorlinks=true,
        linkcolor=blue,
        filecolor=magenta,      
        urlcolor=black,
    }
    \textheight=10in
    \pagestyle{empty}
    \raggedright

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} {#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\subheader} [1] {
    \hspace{2pt}
    \textbf{
        {\hspace*{-18pt}\vspace*{6pt} {#1}}
        \vspace*{-6pt}
    }
    \\
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}

\newcommand{\textslash}{/}
\makeatletter
\DeclareRobustCommand{\textslashsc}{%
  \check@mathfonts
  {\fontsize{\sf@size}{\z@}\selectfont/}%
}
\xapptocmd{\scshape}{\let\textslash\textslashsc}{}{}
\makeatother

\renewcommand{\familydefault}{\sfdefault}

% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
% \rmfamily
\vspace*{-40pt}
\setul{}{0.25pt}
\setulcolor{gray}

%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	{\Huge {Tyler Sedlar}}\\
	\href{https://sedlar.me/}{https:\raisebox{1.1pt}{\textsc{\textbf{\textslash \textslash}}}sedlar.me} $\cdot$ \href{mailto:sedlarizona@gmail.com}{sedlarizona@gmail.com} $\cdot$ (480) 685-1959 $\cdot$ Chandler, AZ\\
\end{center}

%==== Bio ====%
\header{Summary}
A technology enthusiast who is a highly motivated and resourceful individual with the ability to multi-task, meets deadlines, think outside of the box, and enjoy learning.
A hard-working individual with comprehensive knowledge of various languages in software development: Java, Kotlin, NodeJS, Python, and many others.
Not a stranger to other computer related software: G Suite, Microsoft Office Suite, PhotoShop, and more.
\vspace{2mm}

%==== Education ====%
\header{Education}
\textbf{Rio Salado College}\hfill Tempe, AZ\\
AAS Mobile Application Programming \hfill 2018 - 2020\\
\textit{3.73 \href{https://docs.google.com/spreadsheets/d/143DmVdsyjRVbH1ftcySxflvuNjioncAvJpj0vFbzpA8/edit?usp=sharing}{\ul{GPA}}, 3.92 in major}\\

\vspace{2mm}

\textbf{Rio Salado College}\hfill Tempe, AZ\\
Certificate in Programming \& System Analysis \hfill 2018 - 2019\\
\textit{3.92 \href{https://docs.google.com/spreadsheets/d/143DmVdsyjRVbH1ftcySxflvuNjioncAvJpj0vFbzpA8/edit?usp=sharing}{\ul{GPA}}}\\
\vspace{2mm}

%==== Experience ====%
\header{Experience}
\vspace{1mm}

I worked the following positions remotely while in high school for 20 hours per week.

\vspace{1mm}

\textbf{Gold4Players LLC} \hfill Remote\\
Full Stack Developer \hfill 2013 - 2014\\
\vspace{-3mm}
\begin{itemize} \itemsep 1pt
	\item Re-engineered Java bytecode for runtime reflection and proxying
	\vspace{-1mm}
	\item Created a plugin repository web application with PHP
	\vspace{-1mm}
	\item Managed plugins using MySQL and MySQL Workbench
\end{itemize}

\vspace{-2mm}

\textbf{Dequeue Ltd} \hfill Remote\\
Java Software Developer \hfill 2010 - 2013\\
% \vspace{-3mm}
\vspace{-2.5mm}
\begin{itemize} \itemsep 1pt
    \item Created applications for a user-facing video game client
    \vspace{-1mm}
	\item Published applications to a centralized repository for public use
	\vspace{-1mm}
	\item Fixed issues through a continuous public feedback forum
\end{itemize}

%==== Skills ====%
\header{Skills}
\vspace{2mm}
\begin{tabular}{ l l }
    \subheader{Software Development}
    \hspace{-3mm}
	Languages:      & Java, Kotlin, JavaScript, NodeJS, Python, Dart, MySQL, PHP    \\
    \hspace{-3mm}
	Frameworks:     & Flutter, ReactJS, Angular 2, Express, Mongoose, jQuery, Maven, Gradle \\
    \hspace{-3mm}
	Tools:          & Git, MySQL Workbench, VSCode, IntelliJ, Android Studio, Visual Studio
	\vspace{1mm}\\
    \subheader{Computer Literacy}
    \hspace{-3mm}
	Platforms:  & Windows 10, Mac OS X, Linux (Debian, Arch) \\
    \hspace{-3mm}
	Software:   & G Suite, Microsoft Office Suite 2016, PhotoShop CC 2019  \\
    \hspace{-3mm}
	Typing:     & \href{https://data.typeracer.com/misc/badge?user=tsedlar}{\ul{Top 0.1\%}}, 113 WPM Average \\
\end{tabular}
\vspace*{2mm}

%==== Projects ====%
\header{Projects}
{\textbf{\href{https://github.com/TSedlar/MIDI-Mapper}{\ul{MIDI Mapper}}}} \hfill March 2020 \\
\vspace{1mm}
A desktop application that lets you create mappings and macros for MIDI devices. \hfill Kotlin \\ 
Supports controlling streaming software and display visual mappings for some devices. \\
\vspace*{1mm}

{\textbf{\href{https://github.com/TSedlar/InvoiceOrganizer}{\ul{Invoice Organizer}}}} \hfill January 2020 \\
\vspace{1mm}
A program created for a family member who works for a small business. \hfill Kotlin \\ 
This program automatically organizes image files scanned into a document feeder. \\
\vspace*{1mm}

{\textbf{\href{https://sedlar.me/lnreader}{\ul{LNReader}}}} \hfill July 2019 \\
\vspace*{1mm}
A cross-platform mobile application that lets you read and bookmark online light novels. \hfill Flutter \\
Supports content from 9 websites and customization for accessibility.
\vspace*{1mm}

{\textbf{\href{https://github.com/TSedlar/anitrack}{\ul{Anitrack}}}} \hfill June 2019 \\
\vspace*{1mm}
A browser extension that lets you track progress in animated/comic media. \hfill NodeJS \\
Supports tracking media on 25 websites.
\vspace*{1mm}

{\textbf{\href{https://github.com/TSedlar/gr8bar}{\ul{Gr8bar}}}} \hfill November 2017 \\
\vspace*{1mm}
A cross-platform desktop status bar displays your computer's performance statistics \hfill Python \\ and other information in an easy-to-read, aesthetically pleasing display. \\
\vspace*{1mm}

\vspace*{2mm}

\end{document}
